Footpath Planning for Example-driven Procedural Road Networks

### 2020-04-13 paper/paper.tex
Mention utility buildings as a source of area overlap error

% TODO: figure with buildings-slu-cropped
% TODO: mention utility buildings inside compounds, source of marginal errors
% TODO: Turning function example figure for a polygon

@@

>>>>

% TODO: figure with buildings-slu-cropped
% TODO: Turning function example figure for a polygon

@@

The difference in area cover can partially be explained by small utility buildings that are often not represented in the OpenStreetMap dataset. Particularily the residential areas in downtown, Stockholm, are characteristic in that each city block consists of a street front and an open, communal compound in the middle, inside of which there are usually a number of small utility buildings such as bicycle garages, toolsheds and such.
